---
title: "Lung cancer prediction using DNA methylation"
author: "Thomas Battram"
output:
  pdf_document: default
  word_document:
    fig_caption: no
---

```{r setoptions, eval = TRUE, echo = FALSE}
opts_chunk$set(echo = FALSE, 
            warning = FALSE, 
            message = TRUE, 
            cache = FALSE, 
            dpi = 300
            )
```

```{r call_source}
read_chunk("~/Desktop/projects/side_projects/lc_prediction_hunt/report/report.R")
```

``` {r load_data, results = "hide", message = FALSE}
```

```{r roc_setup, results = "hide", message = FALSE}
```

## Goal:

To test the predictive performance of the top 76 CpGs identified in a lung cancer EWAS performed in HUNT, in an independent dataset (NSHDS). 

## Quality control of data:

`r qc_sum[qc_sum$qc_stage == "original_data", "n_sample"]` samples present with DNA methylation data

41 of the 76 probes were present in the 450k dataset.

Probes that have detection p values of >0.01 on 5% or more samples and samples that have detection p values of >0.01 for 5% or more probes were removed. None of the 41 probes were removed. `r qc_sum[qc_sum$qc_stage == "det_p_removed", "n_sample"]` samples were left. Finally, after removing incomplete case-control pairs `r qc_sum[qc_sum$qc_stage == "incomplete_pairs", "n_sample"]` were used in the analysis.

## Models used

Conditional logistic regression code:

``` {r code, echo = TRUE, eval = FALSE}

fit_all <- clogit(LUNG_CANCER_CASE ~ CpG1 + CpG2 + ... + CpGn + strata(CASESET))

fit_ahrr <- clogit(LUNG_CANCER_CASE ~ cg05575921 + strata(CASESET))

```

## Results

``` {r roc_plot, results = "asis", message = FALSE}
```







